---
title: "Schema Remodeling"
output: html_document
---
# Applying Statistical Analysis

I've been doing a lot of Python and pandas in the last couple of notebooks. Now I'm here to analyze the data and see what it can produce. So I'm using the language I'm most familiar with for statistical analysis, R.

Let's start by analyzing the performance of one team, and how they go up against different opponents.
```{r}
# Atlanta Hawks Vs. Cleveland Cavaliers
atl_v_cle <- read.csv('1_Data_Collection/datasets/game_data/atlanta-hawks-cleveland-cavaliers-2024-01-21.csv')
# Atlanta Hawks Vs. Detroit Pistons
atl_v_det <- read.csv('1_Data_Collection/datasets/game_data/atlanta-hawks-detroit-pistons-2023-12-19.csv')
# Atlanta Hawks Vs. Golden State Warriors
atl_v_gsw <- read.csv('1_Data_Collection/datasets/game_data/atlanta-hawks-golden-state-warriors-2024-02-04.csv')
# Atlanta Hawks Vs. LA Lakers
atl_v_lak <- read.csv('1_Data_Collection/datasets/game_data/atlanta-hawks-los-angeles-lakers-2024-01-31.csv')
```

Here are the tables of game recordings to see what type of data I'm working with in this document.

Here is a quick link in case you wish to skip over the data get to my analysis. [Analysis](#Analysis)

## ATL VS CLE

```{r}
atl_v_cle
```

## ATL VS DET
```{r}
atl_v_det
```

## ATL VS GSW
```{r}
atl_v_gsw
```

## ATL VS LAK
```{r}
atl_v_lak
```

## Stating the obvious

We can clearly see a pattern in all these datasets, such as:

- The team with the most points wins...
-

# Analysis

Let's take a look at the most common team in this sample data. The Atlanta Hawks. First, let's start by isolating all these tables to see the Atlanta stats.
```{r}
atl_v_cle
```

```{r}
atl_v_gsw
```

```{r}
atl_v_cle$Reb[atl_v_cle$MIN != 240]
```